Target Markdown

### 2023-10-12 _targets.Rmd
Compute stability component models

```{targets model-to-pred}
list(
  tar_target(model_fw_stab,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"),
      data = mutate(sim_fw, across(c(stab_com, richness), log))
      )),
  tar_target(model_fw_stab_scaled,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"
        ),
      data = sim_fw %>%
        select(-productivity) %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, richness,
              env_stoch, rho, Z,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        )
    ),
  tar_target(model_fw_stab_scaled_coeff,
    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
      as.data.frame() %>%
      rownames_to_column("term") %>%
      as_tibble() %>%
      mutate(term = str_replace(term, "cond\\.", ""))
    ),
  tar_target(pred_data, {
    to <- list(
      richness = log(seq(1, 30, 1)),
      ct_alive = c(.05, .10, .30),
      rho = c(0, .75, 1),
      avg_int_strength = c(.01, .02, .05, .1),
      env_stoch = c(.1, .6),
      w_avg_tlvl = c(1.5, 2, 3),
      Z = c(10, 100),
      h = c(2, 3),
      fw_id = NA) %>% expand.grid()
    ti <- predict(model_fw_stab,
      se.fit = TRUE, re.form = NA,
      newdata = to)
    to$stab_com <- ti$fit
    to$stab_com_se <- ti$se.fit
    to$resp_div <- rho_replacement()[as.character(to$rho)]
    to
    }),
  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(pred_sr_rho_int,
    list(
      rho = seq(0, 1, length.out = 50),
      avg_int_strength = seq(0.01, 0.2, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, avg_int_strength,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .y,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100))))),
  tar_target(pred_sr_rho_tlvl,
    list(
      rho = seq(0, 1, length.out = 50),
      w_avg_tlvl = seq(1.5, 3.5, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, w_avg_tlvl,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .01,
            "h" = 2,
            "w_avg_tlvl" = .y,
            "Z" = 100))))),
  tar_target(pred_sr_rho_ct,
    list(
      rho = seq(0, 1, length.out = 50),
      ct_alive = seq(.02, .3, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, ct_alive,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .y,
            "avg_int_strength" = .01,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100))))),
  tar_target(pred_sr_rho,
    map_dfr(list(pred_sr_rho_int, pred_sr_rho_ct, pred_sr_rho_tlvl),
      ~.x %>%
         pivot_longer(2, names_to = "variable", values_to = "values")
   )
  )
)
```

@@

```{r}
pred_sr_rho_tlvl %>%
  ggplot(aes(x = rho, y = w_avg_tlvl)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg trophic level",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
```

@@

```{r}
pred_sr_rho_ct %>%
  ggplot(aes(x = rho, y = ct_alive)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg trophic level",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
```

```{r}
p_pred_sr_rho_int <- tar_read(pred_sr_rho_int) %>%
  ggplot(aes(x = rho, y = avg_int_strength)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg interaction strength",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
ggsave(
  here("paper", "figures", "p_pred_sr_rho_int.pdf"),
  plot = p_pred_sr_rho_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)

```{r}
tar_load(pred_data)
pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 10,
    h %in% c(3),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 1.5
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(resp_div),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = 1) +
  scale_alpha_manual(values=c(1, 1), guide = "none") +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Response diversity"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

>>>>

```{targets model-to-pred}
list(
  tar_target(model_fw_stab,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"),
      data = mutate(sim_fw, across(c(stab_com, richness), log))
      )),
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : rho : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async, richness), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_scaled,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"
        ),
      data = sim_fw %>%
        select(-productivity) %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, richness,
              env_stoch, rho, Z,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
    ),
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"
        ),
      data = sim_fw %>%
        select(-productivity) %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, rho, Z, h,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(model_fw_stab_scaled_coeff,
    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
      as.data.frame() %>%
      rownames_to_column("term") %>%
      as_tibble() %>%
      mutate(term = str_replace(term, "cond\\.", ""))
    ),
  tar_target(pred_data, {
    to <- list(
      richness = log(seq(1, 30, 1)),
      ct_alive = c(.05, .10, .30),
      rho = c(0, .75, 1),
      avg_int_strength = c(.01, .02, .05, .1),
      env_stoch = c(.1, .6),
      w_avg_tlvl = c(1.5, 2, 3),
      Z = c(10, 100),
      h = c(2, 3),
      fw_id = NA) %>% expand.grid()
    ti <- predict(model_fw_stab,
      se.fit = TRUE, re.form = NA,
      newdata = to)
    to$stab_com <- ti$fit
    to$stab_com_se <- ti$se.fit
    to$resp_div <- rho_replacement()[as.character(to$rho)]
    to
    }),
  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(fix_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(pred_sr_rho_int,
    list(
      rho = seq(0, 1, length.out = 50),
      avg_int_strength = seq(0.01, 0.2, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, avg_int_strength,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .y,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100))))),
  tar_target(pred_sr_rho_tlvl,
    list(
      rho = seq(0, 1, length.out = 50),
      w_avg_tlvl = seq(1.5, 3.5, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, w_avg_tlvl,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .01,
            "h" = 2,
            "w_avg_tlvl" = .y,
            "Z" = 100))))),
  tar_target(pred_sr_rho_ct,
    list(
      rho = seq(0, 1, length.out = 50),
      ct_alive = seq(.02, .3, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, ct_alive,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .y,
            "avg_int_strength" = .01,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100))))),
  tar_target(pred_sr_rho,
    map_dfr(list(pred_sr_rho_int, pred_sr_rho_ct, pred_sr_rho_tlvl),
      ~.x %>%
         pivot_longer(2, names_to = "variable", values_to = "values")

@@

@@

```{r}
tar_load(pred_data)
pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 10,
    h %in% c(3),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 1.5
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(resp_div),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = 1) +
  scale_alpha_manual(values = c(1, 1), guide = "none") +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Response diversity"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
